---
title: "Statistical models for Wang et al. (2021) - Reading & Writing"
date: "3/1/2021"
output:
  html_document:
    css: style.css
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
packages = read.csv('requirements.txt', header = F)[[1]]
lapply(packages, require, ch = T)
load('./data/data.Rda')
source('./scripts/logits.R')
```



## Overview of outliers
There were two participants that stood out as outliers based on their accuracy averaged across all trials: `3` and `46`. These participants were removed based on their performance (`272` trials total).

Trials where the response times were 3SDs above the mean on RT were removed (`81` trials total for these outliers, distributed approximately evenly across the four conditions). Extremely fast trials were removed as well - those that occurred faster than `300 ms` (resulting in `50` observations being removed).

Trials associated with four targets were removed due to the clear discontinuity present in their average accuracy (targets `19`, `16`, `94`, and `93`). These targets were all from the semantic and radical conditions (`204` observations in total for these four targets).

More detailed information about the process of designating outliers in the supplementary information provided.

```{r outliers}
outlier_participants_by_accuracy = c(3, 46)
outlier_targets_by_accuracy = c(16, 19, 93, 94)
high_cutoff_rt = 2742.114
low_cutoff_rt = 300

d = d %>% 
  mutate(outlier = ifelse(subnum %in% outlier_participants_by_accuracy | target_id %in% outlier_targets_by_accuracy | rt > high_cutoff_rt | rt < low_cutoff_rt, TRUE, FALSE))
```

Based on these outliers ```nrow(filter(d, outlier == T))``` trials were excluded for analysis, which amounts to ```r nrow(filter(d, outlier == T))/nrow(d)```% of the data.

## Accuracy
### Descriptive statistics for accuracy

```{r accuracy_descriptives}
d %>% 
  filter(outlier == F) %>% 
  group_by(target_type) %>% 
  summarise(Accuracy = mean(accuracy),
            SD = sd(accuracy)) %>% 
  kable()

```

### Statistical model for accuracy

```{r accuracy}
focal_conditions = c('unrelated', 'semantic')

model_accuracy = d %>% 
  filter(outlier == F) %>% 
  filter(target_type %in% focal_conditions) %>% 
  mutate(condition = case_when(target_type == 'semantic' ~ 1, TRUE ~ 0)) %>% 
  glmer(accuracy  ~ condition + (1 | subnum) + (1 | target_id), family = 'binomial', data = .)

summary(model_accuracy)

predictor_probability(model_accuracy, 'condition', return_unit_difference = T)
```

### Plot of statistical model for accuracy

```{r accuracy_graph}

x = expand.grid(condition = c(0, 1))
y = predictSE(model_accuracy, newdata = x, se.fit = TRUE, type = "response")
predictions = cbind(x, y) %>% 
  mutate(condition = case_when(condition == 0 ~ 'Unrelated',
                               TRUE ~ 'Semantic')) %>% 
  rename(Condition = condition,
         Probability = fit,
         SE = se.fit)

plot_data = d %>% 
  filter(outlier == FALSE) %>% 
  filter(target_type %in% focal_conditions) %>% 
  group_by(subnum, target_type) %>% 
  summarise(Probability = mean(accuracy)) %>% 
  ungroup() %>% 
  mutate(target_type = recode(target_type, 'semantic' = 'Semantic', 'unrelated' = 'Unrelated')) %>% 
  rename(Condition = target_type,
         Participant = subnum)

COLORS = c('Semantic' = 'firebrick', 'Unrelated' = 'goldenrod')

predictions %>% 
  ggplot(aes(Condition, Probability, fill = Condition)) +
  geom_bar(stat = 'identity', width = .75) +
  geom_errorbar(aes(ymin = Probability - SE, ymax = Probability + SE),
                width = .2) +
  scale_fill_manual(values = COLORS) +
  geom_point(data = plot_data, size = .5, color = 'grey26', position = position_jitter(width = .03, height = .02)) +
  coord_cartesian(ylim = c(.7, 1.03)) +
  labs(y = 'Proportion correct') +
  expand_limits(y = 20) +
  theme_classic() +
  theme(legend.position = 'none')

```

## RT
### Descriptive statistics for RT

```{r rt_descriptives}
d %>% 
  filter(outlier == F) %>% 
  filter(accuracy == 1) %>% 
  group_by(target_type) %>% 
  summarise(RT = mean(rt),
            SD = sd(rt), 
            max_ = max(rt), 
            min_ = min(rt)) %>%
  knitr::kable()

```


### Statistical model for RT

```{r rt}
model_rt = d %>% 
  filter(outlier == F) %>% 
  filter(accuracy == 1) %>% 
  filter(target_type %in% focal_conditions) %>% 
  mutate(condition = case_when(target_type == 'semantic' ~ 1, TRUE ~ 0)) %>% 
  lmer(rt  ~ condition + (1 | subnum) + (1 | target_id), data = .)

summary(model_rt)
anova_rt = car::Anova(model_rt, type=3, test = "F")
anova_rt
```

### Plot of statistical model for RT

```{r}

x = expand.grid(condition = c(0, 1))
y = predictSE(model_rt, newdata = x, se.fit = TRUE, type = "response")
predictions = cbind(x, y) %>% 
  mutate(condition = case_when(condition == 0 ~ 'Unrelated',
                               TRUE ~ 'Semantic'),
         RT_ = round(fit, digits = 2)) %>% 
  rename(Condition = condition,
         RT = fit,
         SE = se.fit)

plot_data = d %>% 
  filter(outlier == FALSE) %>% 
  filter(accuracy == 1) %>% 
  filter(target_type %in% focal_conditions) %>% 
  mutate(target_type = recode(target_type, 'semantic' = 'Semantic', 'unrelated' = 'Unrelated')) %>% 
  select(Condition = target_type, RT = rt)

COLORS = c('Semantic' = 'firebrick', 'Unrelated' = 'goldenrod')

predictions %>% 
  ggplot(aes(Condition, RT, fill = Condition)) +
  geom_bar(stat = 'identity', width = .75) +
  scale_fill_manual(values = COLORS) +
  geom_point(data = plot_data, size = .01, color = 'grey26', 
             position = position_jitter(width = .03, height = .02)) +
  geom_errorbar(aes(ymin = RT - SE, ymax = RT + SE),
                width = .2) +
  geom_text(aes(label = RT_, vjust = 7, size = 9)) +
  labs(y = 'Response time (ms)') +
  expand_limits(y = 20) +
  theme_classic() +
  theme(legend.position = 'none')

```





